MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-04-21 latex/paper/paper.tex
dsp cascades

    \textbf{CARRY Chains} \quad
        These CARRY4 blocks can be chained across SLICEs to implement wide adders efficiently. 
        The CARRY4 BELs \emph{must} be chained vertically consecutively across SLICEs as the Carry-In (CI) and Carry-Out (CO) pins can only be routed this way. 
        These CARRY4 BELs will also be connected to LUTs and FFs, and should be placed in the same Site whenever possible to minimize wirelength. 
        Shown in figure \ref{fig:carry_cell_group} shows how a CARRY4 chain and associated LUTs and FFs can be placed across SLICEs.

@@

        {
            \centering
            \includegraphics[width=4.0cm]{figures/carry_chain_placement.png}
            \includegraphics[width=4.0cm]{figures/carry_chain_routes_3.png}
            \captionof{figure}{
                A CARRY4 chain of size 3 placed across 3 SLICEs.
                \textbf{Left:} Simplified view, \textbf{Right:} As shown in the Vivado device viewer.
            }
            \label{fig:carry_cell_group}
        }

    \textbf{DSPs} \quad

    \textbf{DSP Cascades} \quad

>>>>

    \textbf{CARRY Chains} \quad
        These CARRY4 blocks can be chained across SLICEs to implement wide adders efficiently. 
        The CARRY4 BELs \emph{must} be chained vertically consecutively across SLICEs as the Carry-In (CI) and Carry-Out (CO) pins can only be routed this way. 
        These CARRY4 BELs may also be directly connected to LUTs and FFs, and should be placed in the same Site whenever possible to minimize wirelength. 
        Shown in figure \ref{fig:carry_cell_group} shows how a CARRY4 chain and associated LUTs and FFs can be placed across SLICEs.

@@

        {
            \centering
            \includegraphics[valign=c, width=4.0cm]{figures/carry_chain_placement.png}
            \includegraphics[valign=c, width=4.0cm]{figures/carry_chain_routes_3.png}
            \captionof{figure}{
                A CARRY4 chain of size 3 placed across 3 SLICEs.
                \textbf{Left:} Simplified view, \textbf{Right:} As shown in the Vivado device viewer.
            }
            \label{fig:carry_cell_group}
        }

    \textbf{DSPs} \quad 
        FPGAs are often used as low latency Digital Signal Processing (DSP) accelerators. 
        Common DSP subsystems like Finite Impulse Response (FIR) filters, Fast Fourier Transform (FFTs), and convolutional neural nets (CNNs) demand fast large scale multiply-accumulate (MAC) capabilities. 
        The 7-Series arhictecture integrates DSP BELs into the logic fabric called DSP48E1 that can facilitate MAC efficiently.

        {
            \centering
            \includegraphics[width=\columnwidth]{figures/dsp_diagram.png}
            \captionof{figure}{
                Basic DSP48E1 Slice Functionality
            }
            \label{dsp_diagram}
        }

    \textbf{DSP Cascades} \quad 
        Higher level DSP functions are supported by cascading DSP48E1 slices in a DSP48E1 column.
        Much like CARRY4 chains, DSP48E1 cascades must necessarily be placed vertically consecutively across DSP48E1 Sites. 
        They are connected by three 48-bit signal busses: ACOUT to ACIN, BCOUT to BCIN, PCOUT to PCIN.
        These signal busses run directly between the vertical DSP48E1 slices without burdening the general routing resources. 
        The ability to cascade this way provides a high-performance and low-power implementation of DSP filter functions.

        {
            \centering
            \includegraphics[valign=c, width=3.0cm]{figures/dsp_cascade_placement.png}
            \includegraphics[valign=c, width=4.0cm]{figures/dsp_cascade_routed.png}
            \captionof{figure}{
                A DSP48E1 cascade of size 2 placed across 2 DSP48E1 Sites.
                \textbf{Left:} Simplified view, \textbf{Right:} As shown in the Vivado device viewer.
            }
        }
